Revisiting the Relationship between Short-Chain Fatty Acids, the Microbiota, and Colorectal Tumors

### 2018-08-08 submission/manuscript.Rmd
update conclusion

Our observations found no difference in SCFA concentration, their utility as a classification tool, or for genes of enzymes involved in SCFA synthesis between individuals without colon tumors and patients with either adenoma or carcinoma tumors. Although these results are different than other reports in the literature, they do align with the randomized controlled trials that have tested fiber use in preventing colorectal tumor recurrence. Additionally, these observations suggest that resident microbes that are not involved in SCFA production may be the important resident community members involved with preventing tumorigenesis. By focusing on the alternative mechanisms that are associated with these non-SCFA producing resident microbes, the identification of more promising therapeutic options for use in treating colorectal cancer may be found.

>>>>

Our observations found no difference in SCFA concentration or in genes encoding enzymes involved in their production between individuals without colon tumors and patients with either adenoma or carcinoma tumors. The SCFA concentration also did not improve classification of adenoma or carcinoma tumors. The most important OTUs to these models classifying patients with adenomas or carcinomas were mostly not associated with SCFA production. Although these results are different than other reports in the literature, they do align with the randomized controlled trials that have tested fiber use in preventing colorectal tumor recurrence. Additionally, these observations suggest that resident microbes that are not involved in SCFA production may be the important resident community members involved with preventing tumorigenesis. By focusing on alternative mechanisms that are associated with these non-SCFA producing resident microbes or SCFA effects on distinct colorectal cancer groups the identification of more promising therapeutic options for use in treating colorectal cancer may be found.
